A Formal Model of Checked C

### 2023-01-20 sandp23/evaluation.tex
Fixing eval and intro

Our evaluation of ~\systemname{} with NO-OP Sandbox was performed on two programs with the largest overheads in our dataset. With parsons, we see an average run-time overhead of 1.94\% as is expected as parsons (($T_{Pr}$)) gave us an overhead of only 9\%. With TinyBigNum, we see an overhead of 54.7\%, and is expected referring to the figure ~\ref{fig:microbenchmarks}, as TinyBigNum is pointer intensive with pointer operations inside nested loops.     
This shows that~\systemname{} fundamentally has the least overhead.
%The second set of bars in~\fig{fig:runtimeoverhead} shows the runtime overhead. The overhead is negligible in all cases.
%This shows that~\systemname{} fundamentally has the least overhead.
%We modify the instrumentation on~\code{tainted} pointers to check for a valid pointer (instead of within sandbox bounds) -- this will add the same amount of checks as in sandboxing case, but the comparison values will be different.
%The marked \textcolor{red}{red} set of bars in~\fig{fig:runtimeoverhead} shows the runtime overhead. The overhead is negligible in all cases.
%This shows that~\systemname{} fundamentally has the least overhead.

>>>>

We performed our experiment on~\texttt{Persons} and~\texttt{TinyBigNum}, the two programs with the largest overheads in our dataset.
As expected, the runtime overhead of~\texttt{Persons} is 1.94\% -- which shows that the sandbox is the main contributor to the overhead.
For~\texttt{TinyBigNum}, the overhead is a bit higher at 54.7\%, our analysis shows that the overhead is because we tainted the main input buffer, which is processed in loops.
This leads to additional checking for every loop iteration resulting in higher overhead.
Another reason is that in the current implementation, our instrumentation is performed at the end after all optimization passes; thus, none of the instrumentation is optimized.
We plan to move our instrumentation before the optimization passes and exploit them to optimize further and decrease the runtime overhead.

%Our evaluation of~\systemname{} with NO-OP Sandbox was performed on two programs with the largest overheads in our dataset. With parsons, we see an average run-time overhead of 1.94\% as is expected as parsons (($T_{Pr}$)) gave us an overhead of only 9\%. With TinyBigNum, we see an overhead of 54.7\%, and is expected referring to the figure ~\ref{fig:microbenchmarks}, as TinyBigNum is pointer intensive with pointer operations inside nested loops.     
%This shows that~\systemname{} fundamentally has the least overhead.
%The second set of bars in~\fig{fig:runtimeoverhead} shows the runtime overhead. The overhead is negligible in all cases.
%This shows that~\systemname{} fundamentally has the least overhead.
%We modify the instrumentation on~\code{tainted} pointers to check for a valid pointer (instead of within sandbox bounds) -- this will add the same amount of checks as in sandboxing case, but the comparison values will be different.
%The marked \textcolor{red}{red} set of bars in~\fig{fig:runtimeoverhead} shows the runtime overhead. The overhead is negligible in all cases.
%This shows that~\systemname{} fundamentally has the least overhead.

### 2023-01-20 sandp23/introduction.tex
Fixing eval and intro

\myparagraph{\systemname Type System, Formalism and Compiler}
We present a type system that integrates tainted types with~\checkedc and provides additional guarentees---the~\emph{non-crashing} and \emph{non-exposure} guarantees,~\ie a well-typed~\systemname program can never crash due to spatial safety violations,
as well as \ucregion code cannot directly observe a checked pointer address.
%no \cregion pointer addresses will be leaked in
%\ucregion code
We extend the \checkedc compiler to support the type system and
formalize it by extending~\checkedc formalism~\citet{li22checkedc} with the non-crashing and non-exposure guarantees.
We formally prove theorems related to the two guarantees and use model-based randomized testing (CITE) to certify the simulation relation between the~\systemname semantics and its compiler formalism.
To the best of our knowledge,~\systemname is the first C(-like) language and compiler formalism with the program partitioning mechanism.

>>>>

\myparagraph{\systemname Type System, Formalism and Compiler}
We present a type system that integrates tainted types with~\checkedc and provides additional guarentees---the~\emph{non-crashing} and \emph{non-exposure} guarantees,~\ie a well-typed~\systemname program can never crash due to spatial safety violations,
as well as \ucregion code cannot directly observe a checked pointer address.
%no \cregion pointer addresses will be leaked in
%\ucregion code
We extend the \checkedc compiler to support the type system and
formalize it by extending~\checkedc formalism~\cite{li22checkedc} with the non-crashing and non-exposure guarantees.
We formally prove theorems related to the two guarantees and use model-based randomized testing \cite{Pierce:SF4} to certify the simulation relation between the~\systemname semantics and its compiler formalism.
To the best of our knowledge,~\systemname is the first C(-like) language and compiler formalism with the program partitioning mechanism.
